\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-06-15 doc/USER_MANUAL/05_running_the_solver.tex
nice bug fix by Lei Zhang in src/shared/read_parameter_file.F90

In addition to inbuild source time function, the solver can also use an external source time function defined by the user. This option can be
activated by setting   \texttt{EXTERNAL\_SOURCE\_FILE} to true in \texttt{Par\_File} and by adding the name of the file
containing the source time function at the end of \texttt{FORCESOLUTION} or \texttt{CMTSOLUTION} files. The source time function file must
contain 2 columns with the current time and the amplitude of the soure function. The time step must be the same as used for the
simulation. Note  when the  \texttt{EXTERNAL\_SOURCE\_FILE} is set to false then the line with the external source time function file must not appear in
the files  \texttt{FORCESOLUTION} and \texttt{CMTSOLUTION} otherwise the solver will exit with an error.
When using an external source file, you can still set up the source location and directivity as in the default case.
In the FORCESOLUTION file: you set "latorUTM", "longorUTM" and "depth" to define the position of your point source. Then if you want to define a directivity, then change the following lines: "component dir vect source E", "component dir vect source N" and "component dir vect source Z\_UP". What you are doing is simply that you define the source position and directivity the same way as in the default case, but in addition you are specifying the path to read in a non-default source time function from an external file.

>>>>

In addition to inbuild source time function, the solver can also use an external source time function defined by the user. This option can be
activated by setting   \texttt{EXTERNAL\_SOURCE\_FILE} to true in \texttt{Par\_File} and by adding the name of the file
containing the source time function at the end of \texttt{FORCESOLUTION} or \texttt{CMTSOLUTION} files.
The source time function file must contain the value of the time step on its first line, and then a single column with the amplitude of the source time function for all the time steps.
The time step must be exactly the same as that used for the simulation.
Note  when the  \texttt{EXTERNAL\_SOURCE\_FILE} is set to false then the line with the external source time function file must not appear in
the files  \texttt{FORCESOLUTION} and \texttt{CMTSOLUTION} otherwise the solver will exit with an error.
When using an external source file, you can still set up the source location and directivity as in the default case.
In the FORCESOLUTION file: you set "latorUTM", "longorUTM" and "depth" to define the position of your point source. Then if you want to define a directivity, then change the following lines: "component dir vect source E", "component dir vect source N" and "component dir vect source Z\_UP". What you are doing is simply that you define the source position and directivity the same way as in the default case, but in addition you are specifying the path to read in a non-default source time function from an external file.
